---
title: "Extracting Features with Communication"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{extracting-features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(communication)
library(magrittr)
```



In order to extract features from a audio file, two parameters are required, 
the name of the file and a configuration. 


## Config

The configuration is contained in an audio_config object. `createConfig()` create 
the basis for the object. Parameters `frameSize` and `frameStep` are used to 
separate the raw audio data.

```{r}
audioConfig <- createConfig(frameSize = 0.025, frameStep = 0.0125 )
```

Components are added over the basis and indicate 
the features to be extracted. For example, mean-crossing rate, 
zero-crossing rate, dc, amax, intensity and loudness can be extracted from frames 
themselves. For each added component, input and output must be 
explicitly declared. Users can choose the name of output.

```{r}
audioConfig <- audioConfig %>%
  mcr('frames','mcr') %>%
  zcr('frames','zcr')  %>%
  dc('frames','dc') %>%
  a_max('frames','amax') %>%
  intensity('frames','intensity') %>%
  loudness('frames','loudness') 
```


Some components require intermediate steps. For example, 
 to extract 13  Mel-frequency cepstrum coefficients, 
 config must also add a fourier transform, mag/phase representation, and 
 mel spectogram with parameters low frequency equal to 20, high frequency, 8000,
 and 26 bands.
 
```{r}
 audioConfig <- audioConfig %>%
  fastFourierTransform(input = 'frames',output = 'fourierTransform') %>%
  magPhase(input = 'fourierTransform',output = 'magphase') %>%
  melSpec('magphase','melspec', lofreq = 20, hifreq = 8000, nBands = 26) %>%
  mfcc(firstMfcc = 1, lastMfcc = 13)
```


Given the extracted features, derivatives can be added as well. In this case,
 we utilize the component `delta`. It is not required to add names for outputs.
 In this case, outputs will have the same name as input with "de_" added.
 For instance, a delta for "mcr" would receive the name "de_mcr".
 
```{r}
audioConfig <- audioConfig %>%
  delta(input = "mcr")
```

In order to extract automatically deltas for different features, it is possible to use
`add_components` 

```{r}
audioConfig <- audioConfig %>%
  addComponents(delta, c("mcr","zcr","intensity","loudness"))

```


To check the audio_config object, it it possible to plot it or print it.







```{r}
#getEdges(audioConfig)
```


